Computing the evolution and detectability of stellar-origin gravitational-wave sources\\in space-based detectors using the LEGWORK python package

### 2021-12-06 src/ms.tex
update title based on JOSS comments

\title{LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors}

>>>>

\title{Computing the evolution and detectability of stellar-origin gravitational-wave sources\\in space-based detectors using the LEGWORK python package}
